Evaluating machine translation for assimilation

### 2015-02-19 2015-eamt-assim/2015-eamt-assim.tex
+1 comment
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59016 72bbbca6-d526-0410-a7d9-f06f51895060

This section discusses the reasoning behind the gap-filling method and task structure. The gap-filling method 
of evaluating machine translation for assimilation purposes is based on the following notion: a reader's understanding 
of a given text correlates with the number of keywords they are able to correctly restore in the text. Therefore, the 
base of an assimilation task is a (reference) sentence, where some of the keywords are blacked out, or removed. The sentence 
is produced by a human (as opposed to machine-translated), and it is in the language known to evaluators, which is also 
the \emph{target language} of the machine translation system.

The additional elements of the task are what we call hints, or extra sentences that help the participant to understand 
the main sentence. There are two types of hints: first, the \emph{source}, which is the same sentence as \emph{reference}, 
also human-produced, but in the source language of the pair. The second type is the \emph{machine-translated} hint, which 
comes from the machine translation of the \emph{source } sentence.

>>>>

This section discusses the reasoning behind the gap-filling method and task structure. The gap-filling method 
of evaluating machine translation for assimilation purposes is based on the following notion: a reader's understanding 
of a given text correlates with the number of keywords they are able to correctly restore in the text. Therefore, the 
base of an assimilation task is a (reference) sentence, where some of the keywords are blacked out, or removed. The sentence 
is produced by a human (as opposed to machine-translated), and it is in the language known to evaluators, which is also 
the \emph{target language} of the machine translation system.
\comment{FMT: It would also be nice to have a screenshot here}
The additional elements of the task are what we call hints, or extra sentences that help the participant to understand 
the main sentence. There are two types of hints: first, the \emph{source}, which is the same sentence as \emph{reference}, 
also human-produced, but in the source language of the pair. The second type is the \emph{machine-translated} hint, which 
comes from the machine translation of the \emph{source } sentence.
